Constraining the Interiors of Asteroids Through Close Encounters: Appendices

### 2022-08-26 paper/main.tex
Started supplemental material

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{colortbl}
\usepackage{dsfont}
\usepackage{siunitx}
\usepackage{bm}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphbox}
\usetikzlibrary{arrows.meta}

\renewcommand{\unit}[1]{\bm{\hat{#1}}}
\newcommand{\parens}[1]{\left( #1 \right)}
\newcommand{\brackets}[1]{\left[ #1 \right]}
\newcommand{\quat}[1]{\widetilde{\bm{#1}}}

@@

  \caption{Cross-sectional slices of the density distributions extracted via the finite element model for the asymmetric (\textit{top two rows}) and symmetric (\textit{bottom two rows}) uniform-density reference asteroids. The finite element model (\textit{first and third rows}) and the lumpy model (\textit{second and fourth rows}) are employed. From left to right, the densities (divided by the average density), deviations from the true density, uncertainties, and significance of the deviations are plotted. These figures are available in animated form in the Supplemental Data. Extracted densities are generally within 10\% of the truth.}
  \label{fig:den-uniform}
\end{figure*}

@@

The asteroid simulation, fit process, and density moment extraction code are available on \href{https://github.com/jack-dinsmore/asteroid-tidal-torque}{GitHub}. Please contact JTD with questions.

>>>>

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{xcolor}
\usepackage{tikz}
\usepackage{bm}
\usepackage{caption}
% \usepackage{subcaption}
\usepackage{graphbox}
\usetikzlibrary{arrows.meta}

\newcommand{\unit}[1]{\bm{\hat{#1}}}
\newcommand{\parens}[1]{\left( #1 \right)}
\newcommand{\brackets}[1]{\left[ #1 \right]}
\newcommand{\quat}[1]{\widetilde{\bm{#1}}}

@@

  \caption{Cross-sectional slices of the density distributions extracted via the finite element model for the asymmetric (\textit{top two rows}) and symmetric (\textit{bottom two rows}) uniform-density reference asteroids. The finite element model (\textit{first and third rows}) and the lumpy model (\textit{second and fourth rows}) are employed. From left to right, the densities (divided by the average density), deviations from the true density, uncertainties, and significance of the deviations are plotted. These figures are available in animated form in the Supplementary Material. Extracted densities are generally within 10\% of the truth.}
  \label{fig:den-uniform}
\end{figure*}

@@

The asteroid simulation, fit process, and density moment extraction code are available on GitHub\footnote{\url{https://github.com/disruptiveplanets/asteroid-interior-constraints}}. Please contact JTD with questions.

### 2022-08-26 paper/supplement.tex
Started supplemental material

\appendix

@@

\begin{table}
  \centering
  \begin{tabular}{c|ccccccc}
    \hline
    $\ell$ & $\Re K_{\ell 3}$ & $\Im K_{\ell 3}$ & $\Re K_{\ell 2}$ & $\Im K_{\ell 2}$ & $\Re K_{\ell 1}$ & $\Im K_{\ell 1}$ & $K_{\ell 0}$ \\ \hline
    0 &  &  &  &  &  &  & -\\ 
    1 &  &  &  &  & x & y & z\\ 
    2 &  &  & - & x,y & y,z & x,z & -\\ 
    3 & x,z & y,z & z & x,y,z & x & y & z\\ \hline
  \end{tabular}
  \caption{Axes of mirror symmetry that imply zeroed density moments. For example, for mirror symmetries along $\unit y$ or $\unit z$, $\Im K_{32}=0$. Mirror symmetry along $\unit x$ means $\rho_\mathcal{A}(x, y, z) = \rho_\mathcal{A}(-x, y, z)$. Dashes indicate that none of the mirror symmetries zero the moment in question. Since $r^2>0$ for $r\neq 0$, no symmetries set $a_\mathcal{A}=0$ either.}
  \label{tab:klm-symmetries}
\end{table}

@@

Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \citep{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the MOI of the rigid body (or higher order moments of inertia), and to varying degrees of precision. A simple, first-order derivation is also easily computable in terms of the asteroid MOI in the inertial frame.

@@

>>>>

\documentclass[9pt,twocolumn]{article}

\usepackage[T1]{fontenc}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{extsizes}
\usepackage{tikz}
\usepackage{titlesec}
\usepackage{bm}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{graphbox}
\usepackage{authblk}
\usepackage[backend=bibtex, style=authoryear]{biblatex}
\usepackage[top=0.75in,bottom=0.75in,left=0.6in,right=0.6in]{geometry}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usetikzlibrary{arrows.meta}

\newcommand{\unit}[1]{\bm{\hat{#1}}}
\newcommand{\parens}[1]{\left( #1 \right)}
\newcommand{\brackets}[1]{\left[ #1 \right]}
\newcommand{\quat}[1]{\widetilde{\bm{#1}}}
\setlength{\columnsep}{2em}
\renewcommand\floatpagefraction{.55}

\titleformat{\section}
  {\normalsize\bfseries}
  {\thesection}
  {.5em}
  {\MakeUppercase}
\titleformat*{\subsection}{\normalsize\bfseries}

\title{Constraining the Interiors of Asteroids Through Close Encounters: Appendices}

\author[1]{Jack T. Dinsmore}
\author[2]{Julien de Wit}
\affil[1]{Department of Physics, Massachusetts Institute of Technology}
\affil[2]{Department of Earth, Atmospheric, and Planetary Science, Massachusetts Institute of Technology}

\bibliography{asteroids}

\begin{document}

\maketitle

@@

\begin{table}
  \centering
  \small
  \begin{tabular}{c|ccccccc}
    \hline
    $\ell$ & $\Re K_{\ell 3}$ & $\Im K_{\ell 3}$ & $\Re K_{\ell 2}$ & $\Im K_{\ell 2}$ & $\Re K_{\ell 1}$ & $\Im K_{\ell 1}$ & $K_{\ell 0}$ \\ \hline
    0 &  &  &  &  &  &  & -\\ 
    1 &  &  &  &  & x & y & z\\ 
    2 &  &  & - & x,y & y,z & x,z & -\\ 
    3 & x,z & y,z & z & x,y,z & x & y & z\\ \hline
  \end{tabular}
  \caption{Axes of mirror symmetry that imply zeroed density moments. For example, for mirror symmetries along $\unit y$ or $\unit z$, $\Im K_{32}=0$. Mirror symmetry along $\unit x$ means $\rho_\mathcal{A}(x, y, z) = \rho_\mathcal{A}(-x, y, z)$. Dashes indicate that none of the mirror symmetries zero the moment in question. Since $r^2>0$ for $r\neq 0$, no symmetries set $a_\mathcal{A}=0$ either.}
  \label{tab:klm-symmetries}
\end{table}

@@

Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \cite{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the MOI of the rigid body (or higher order moments of inertia), and to varying degrees of precision. A simple, first-order derivation is also easily computable in terms of the asteroid MOI in the inertial frame.

@@

\printbibliography

\end{document}
